---
title: "Notebook"
author: "Hrithik Chauhan"
date: "08/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, warning=FALSE}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(ggthemes)) 
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(highcharter))
suppressPackageStartupMessages(library(corrplot))
col1 <- '#FF8B03'
col2 <- '#20BEFF'
col3 <- '#1DB954'
col4 <- '#FF0000'
```

Let’s see the first few rows of the data file and also glimpse the data file. 

```{r input, message=FALSE, warning=FALSE}
df <- read_csv("consolidated_coin_data.csv")
```
The data includes 83,156 rows and 8 columns.

### Column Names

```{r}
names(df)
```

### Unique Cryptocurrencies in the Dataset 

There are 12 unique cryptocurrencies.

```{r}
unique(df$Currency)
```

### Potential Questions to be Answered

* Cryptocurrency distribution on basis of Trading Volume
* Cryptocurrency distribution on basis of Market Cap
* Correlation between Market Capitalization and Close Price
* Correlation between Trading Volume and Close Price

### Analysis

### Trading Volume Distribution

Tether and Bitcoin got the highest trading volume. And, below is the visualization of distribution;

```{r}
df  %>% 
  arrange(desc(Volume)) %>% 
  select(one_of('Currency','Volume')) %>% 
  hchart('bar',hcaes(Currency, Volume),
          color = col3) %>% 
  hc_title(text = "Cryptocurrency distribution on basis of Trading Volume") %>% 
  hc_add_theme(hc_theme_darkunica())
```
### Market Capitalization Distribution

Bitcoin and Ethereum got the highest market capitalization. And, below is the visualization of distribution;

```{r}
df  %>% 
  arrange(desc(`Market_Cap`)) %>% 
  select(one_of('Currency','Market_Cap')) %>% 
  hchart('bar',hcaes(Currency, Market_Cap),
          color = col4) %>% 
  hc_title(text = "Cryptocurrency distribution on basis of Market Capitalization") %>%
  hc_add_theme(hc_theme_darkunica())
```
### Correlation Analysis

### Correlation between Market Cap and Close Prices of Cryptocurrency

```{r}
df %>% 
  select(c('Market_Cap', 'Close')) %>% 
  cor()
```
### Correlation between Trading Volume and Close Prices of Cryptocurrency

```{r}
df %>% 
  select(c('Volume', 'Close')) %>% 
  cor()
```
### Visualization (Scatter Plot)

```{r}
df %>% 
  select(c('Market_Cap', 'Close')) %>% 
  ggplot(aes(x = Close, y = Market_Cap)) + 
  geom_point( color= col1) +
  geom_smooth(method = lm) +
  labs(title = 'Market Capitalization and Close Prices are Highly Correlated') +
  ggthemes::theme_few() -> ggrest
plotly::ggplotly(ggrest)
```

```{r}
df %>% 
  select(c('Volume', 'Close')) %>% 
  ggplot(aes(x = Volume, y = Close)) + 
  geom_point(color= '#FF8B03') +
  geom_smooth(method = lm) +
  labs(title = 'Trading Volume and Close Price of are Significantly Correlated') + ggthemes::theme_few() -> ggrest1
plotly::ggplotly(ggrest1)
```

### Thank you! You have reached to end of the analysis. 
